
---
title: "Bayesian SEM Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This document demonstrates how to perform Bayesian Structural Equation Modeling (SEM) using attached dataset. Bayesian SEM allows for greater flexibility and incorporates prior knowledge into the modeling process.

---

## Step 1: Load the Data

```{r load-data}
# Load necessary libraries
library(tidyverse)
library(blavaan)

# Load the dataset (assuming it's in the same folder as this Rmd file)
data <- read.csv("bayesian_sem_data.csv")

# Quick look at the data
head(data)
summary(data)
```

---

## Step 2: Define the SEM Model

```{r define-model}
# Define the SEM model
sem_model <- '
  # Latent variables
  Latent_1 =~ Indicator_1_1 + Indicator_1_2 + Indicator_1_3
  Latent_2 =~ Indicator_2_1 + Indicator_2_2 + Indicator_2_3
  Latent_3 =~ Indicator_3_1 + Indicator_3_2 + Indicator_3_3

  # Structural paths
  Latent_2 ~ Latent_1
  Latent_3 ~ Latent_1 + Latent_2
'
```

---

## Step 3: Fit the Bayesian SEM Model

```{r fit-model}
# Fit the Bayesian SEM model
fit <- blavaan::bsem(sem_model, data = data)

# Summary of the model
summary(fit, fit.measures = TRUE, standardized = TRUE)
```

---

## Step 4: Check Model Diagnostics

```{r diagnostics}
# Trace plots
blavaan::traceplot(fit)

# Posterior predictive checking
blavaan::ppcheck(fit)
```

---

## Step 5: Interpret Results

- **Latent Variables**: The model estimates the relationships between latent variables and their indicators.
- **Structural Paths**: The regression paths between latent variables provide insight into their relationships.
- **Bayesian Diagnostics**: Trace plots and posterior predictive checks ensure model convergence and goodness of fit.

---

## Conclusion

This document demonstrates Bayesian SEM, a powerful tool for modeling complex relationships in HF/UX research. Adjust the model and priors to fit your specific dataset and research questions.
